Stochastic blockmodeling of relational event dynamics

### 2012-06-01 docs/experiments.tex
Experiments section.

A variety of real world datasets are used to explore the efficacy of the model.  Each of the following data sets are sequences of dyadic events, where each event has a sender, recipient, and timestamp.

\begin{itemize}
%\item Kiel email: \cite{Ebel2002}
\item Classrooms: TODO describe datasets. Each have about 20 people and 400 events.  \cite{McFarland2001}
\item Eckmann email: dyadic emails.  2000 training events among 88 people and 1300 test events.  \cite{Eckmann2004}
\item Enron email: dyadic emails between months [TODO], 3000 training and 1000 test events among 141 actors \cite{Klimt2004}
%\item Irvine: dyadic interactions among 401 actors each having more than 30 events,  \cite{Opsahl}
\item Tweets from Twitter.com occurring between from May 11, 2009 to January 26, 2012 that contained the hashtag \texttt{\#rstats}.\footnote{Will be made publicly available.}  This hashtag is used to denote messages pertaining to the R statistical computing environment and sometimes statistical discussion more generally.  We collect dyadic events by selecting tweets beginning with the \texttt{@} symbol (called a \emph{mention}), and mark the first mentioned user as the recipient.
Of 28337 total tweets in this time period, 3926 were directed events among a total of 1079 users.
We use the subset of 487 users who participated in more than one event, using a training set of 2000 events and a test set of 1330 events.
\item MIT Reality Mining: phone calls among the 89 recipients between the dates , using of 2000 training events followed by 1000 test events. \cite{Eagle2009}
\end{itemize}

@@

We evaluate the predictive ability of the fitted models by comparing models based on the loglikelihood and recall for held-out data.
Each data set is first split into a training set and a test set, and the loglikelihood of the test set is computed sequentially using Equation \ref{eqn:llk} where $\hat{\lambda}_{i,j}(t_m) = \frac{1}{S}\sum_k \lambda_{i,j}(t_m | \boldsymbol{\beta}^{(k)}, \mathbf{z}^{(k)})$ is averaged using $K$ posterior samples given the training data.
% TODO: We compute both the relational event model likelihood  (\texttt{rem}) as given in Equation \ref{eqn:llk}  and the multinomial likelihood (\texttt{mult}) given in Equation \ref{eqn:multllk}.
% TODO: The latter only measures a model's predictive performance for \emph{what} occurs next, while the former also measures the ability to predict \emph{when} it occurs.

@@

\input{../figs/results-llk3.tex}
\input{../figs/results-recall-5.tex}
\input{../figs/results-recall-20.tex}

%\subsection{Baselines}

>>>>

A variety of real world data sets are used to explore the efficacy of the model.  The following data sets are sequences of dyadic events, where each event has a sender, recipient, and timestamp.  For each data set, we hold out the final $M_{test}$ events for evaluation of the model.

\begin{itemize}
%\item Kiel email: \cite{Ebel2002}
\item Classroom \cite{McFarland2001}: 445 directed communication among 27 people a high
  school classroom collected via participant observation ($M_{test}= 145$).
\item University email \cite{Eckmann2004}: 3300 dyadic emails among 88 people with at least 30
  emails each ($M_{test} = 1300$)
\item Enron email \cite{Klimt2004}: 4000 dyadic emails among 141
  individuals between TODO months ($M_{test} = 1000$)
%\item Irvine: dyadic interactions among 401 actors each having more than 30 events,  \cite{Opsahl}
\item Twitter direct messages: Tweets from Twitter.com occurring between from May 11, 2009 to January 26, 2012 that contained the hashtag \texttt{\#rstats}.  This hashtag is used to denote messages pertaining to the R statistical computing environment and sometimes statistical discussion more generally.  We collect dyadic events by selecting tweets beginning with the \texttt{@} symbol (called a \emph{mention}), and mark the first mentioned user as the recipient.
Of 28337 total tweets in this time period, 3926 were directed events among a total of 1079 users.
We use a subset 4330 events among 487 users who participated in more than one event ($M_{test} = 1330$).\footnote{This dataset will be made publicly available.}
\item MIT Reality Mining \cite{Eagle2009}: 2000 phone calls among the 89 recipients between the dates TODO ($M_{test}= 1000$).
\end{itemize}

@@

We evaluate the predictive ability of the fitted models by comparing models based on the loglikelihood and recall for held-out data.
%Each data set is first split into a training set and a test set, and 
The loglikelihood of the test set is computed sequentially using Equation \ref{eqn:llk} where $\hat{\lambda}_{i,j}(t_m) = \frac{1}{L}\sum_l \lambda_{i,j}(t_m | \boldsymbol{\beta}^{(l)}, \mathbf{z}^{(l)},\mathcal{A}_t)$ is averaged using $L$ posterior samples given the training data.
% TODO: We compute both the relational event model likelihood  (\texttt{rem}) as given in Equation \ref{eqn:llk}  and the multinomial likelihood (\texttt{mult}) given in Equation \ref{eqn:multllk}.
% TODO: The latter only measures a model's predictive performance for \emph{what} occurs next, while the former also measures the ability to predict \emph{when} it occurs.

@@

{ \footnotesize
\input{../figs/results-llk4.tex}
\input{../figs/results-recall-5.tex}
\input{../figs/results-recall-20.tex}
}
%\subsection{Baselines}
